MLPPI Wizard: An Automated Multi-Level Partitioning Tool on Analytical Workloads

### 2017-02-23 mlppi-comsis17/cover-letter.tex
ComSis cover letter

\opening{Dear Prof. Vladimir Kurbalija (or Editor-in-Chief):}

@@

\item Expanded Algorithms: we expand the description of the pre-processing, initial and optimized phase algorithms shortened in the earlier version. Furthermore, this submission contains three additional algorithms as follows:

>>>>

\opening{Dear Prof. Mirjana Ivanovi\'c (Editor-in-Chief):}

@@

\item Expanded Algorithms: we substantially expand the description of the pre-processing, initial and optimized phase algorithms shortened in the earlier version. Furthermore, this submission contains three additional algorithms as follows:
